SunPy - Python for Solar Physics

### 2014-08-28 2-1-Map.tex

\begin{itemize}
\item \textit{Yohkoh} Solar X-ray Telescope (SXT; \citealp{1991SoPh..136....1O, 1991SoPh..136...37T}),
\item Solar and Heliospheric Observatory (\textit{SOHO}; \citealp{domingo1995}) Extreme Ultraviolet Telescope (EIT; \citealp{1995SoPh..162..291D})
\item \textit{SOHO} Large Angle Spectroscopic COronagraph (LASCO; \citealp{1995SoPh..162..357B})
\item \textit{RHESSI} - Reuven Ramaty High Energy Solar Spectroscopic Imager \citep{2002SoPh..210....3L},
\item Solar TErrestrial RElations Observatory (\textit{STEREO}; \citealp{2005AdSpR..36.1483K}) Extreme Ultraviolet Imager (EUVI; \citep{2004SPIE.5171..111W})
\item \textit{STEREO} CORonagraph 1/2 (COR 1/2; \citealp{2002AdSpR..29.2017H})
\item \textit{Hinode} XRT - X-Ray Telescope \citep{2007SoPh..243....3K, 2007SoPh..243...63G}.
\item PRojects for On Board Autonomy 2 (\textit{PROBA2}; \citealp{2013SoPh..286....5S}) Sun Watcher Active Pixel (SWAP; \citealp{2013SoPh..286...43S})
\item \textit{SDO} AIA and HMI: Helioseismic Magnetic Imager, \citep{2012SoPh..275..207S}
\item Interface Region Imaging Spectrograph (\textit{IRIS}; \citealp{2011SPD....42.1512L}) SJI (slit-jaw imager) frames.           
\end{itemize}

>>>>

\begin{itemize}
\item \textit{Yohkoh} Solar X-ray Telescope (SXT, \citealp{1991SoPh..136....1O, 1991SoPh..136...37T}),
\item Solar and Heliospheric Observatory (\textit{SOHO}, \citealp{domingo1995}) Extreme Ultraviolet Telescope (EIT; \citealp{1995SoPh..162..291D})
\item \textit{SOHO} Large Angle Spectroscopic COronagraph (LASCO, \citealp{1995SoPh..162..357B})
\item \textit{RHESSI} - Reuven Ramaty High Energy Solar Spectroscopic Imager \citep{2002SoPh..210....3L},
\item Solar TErrestrial RElations Observatory (\textit{STEREO}, \citealp{2005AdSpR..36.1483K}) Extreme Ultraviolet Imager (EUVI, \citep{2004SPIE.5171..111W})
\item \textit{STEREO} CORonagraph 1/2 (COR 1/2, \citealp{2002AdSpR..29.2017H})
\item \textit{Hinode} XRT - X-Ray Telescope \citep{2007SoPh..243....3K, 2007SoPh..243...63G}.
\item PRojects for On Board Autonomy 2 (\textit{PROBA2}, \citealp{2013SoPh..286....5S}) Sun Watcher Active Pixel (SWAP; \citealp{2013SoPh..286...43S})
\item \textit{SDO} AIA and Helioseismic Magnetic Imager, (HMI, \citealp{2012SoPh..275..207S})
\item Interface Region Imaging Spectrograph (\textit{IRIS}, \citealp{2011SPD....42.1512L}) SJI (slit-jaw imager) frames.           
\end{itemize}
